The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-08 main.tex
small tweaks to authors footnote

\author{Astropy Project}
\noaffiliation
\footnote{The author list has three parts: the 13 authors that made significant contributions to the  writing of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributions to the \astropy Project in alphabetical order.  The position in the author list does not correspond to contributions to the \astropy Project as a whole.  A more complete list of contributors to the core package can be found in the \href{https://github.com/astropy/astropy/graphs/contributors}{package repository}, and at the \href{http://www.astropy.org/team.html}{\astropy team webpage}.}

>>>>

\author{Astropy Project}
\noaffiliation
{\let\thefootnote\relax\footnote{{The author list has three parts: the authors that made significant contributions to the writing of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributors to the \astropy Project in alphabetical order. The position in the author list does not correspond to contributions to the \astropy Project as a whole. A more complete list of contributors to the core package can be found in the \href{https://github.com/astropy/astropy/graphs/contributors}{package repository}, and at the \href{http://www.astropy.org/team.html}{\astropy team webpage}.}}}
